Supplementary appendix

### 2019-07-24 paper3_APPENDIX_revision_01.Rmd
Add files via upload

---
title: "Supplementary appendix"
author: '**Saar Alon-Barkat**, PhD candidate; the Hebrew University of Jerusalem;   saar.barkat@mail.huji.ac.il'
date: " "
output:
  html_document:
    theme: flatly
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

@@

```{r , include=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(stargazer)
library(car)
library(broom)
library(kableExtra)
library(sjPlot)
library(ggthemes)
library(ggpubr)
library(lmtest)
library(sandwich)

@@

# Properties of the selected cities

@@

Notes:
Data for all cities, except for Qiryat-Hayiim, is retrived from the Central Bureau of Statistics data file of local authorities in Israel of 2015. Qiryat-Hayiim is considered, formally, a neighborhood within the jurisdiction of Haifa, although it is geographically seperated from the rest of the city. Therefore, it is included in the official statistical data within Haifa. The population of Qiryat-Hayiim is based on a document of statistical data for neighborhoods in Haifa for 2015, retrived from the website of the municipality of Haifa.

@@

@@

@@

"The person presented in the image is familiar to me" (1=weakly agree; 7=strongly agree)

@@

@@

@@

@@

This section aims to assess the concernt that participants did not accept the authenticity of the weak, fictional policy plan, and did not find it reliable, and as a results lost trust in the rest of the survey. To assess that risk, I took advantage of the fact that the order in which the strong and weak policies were presented was randomized. Accordingly, half of the participants saw a weak plan first, and thereafter a strong plan, and for the other half it was the opposite. Hence, I examined whether the the strong policy was evaluated differently when it was presented first (which means that participants at that point did not sea weak policy yet and did not question the reliability of the survey), then when it was presented second (after they already saw a fictional policy). This comparison, accross the two policies, is graphically presented in the following plot. It shows that the differences between the means and distributions of the first and the second policy are relatively small and insignificant. The small increase between the first and second round may be explained be the fact that participants used the first (weak) policy as a benchmark, and therefore compared the second policy with the first one. Altogether, these test tend to indicate that participants' exposure to the fictional weak policy did not have a strong influence on their answers to the subsequent questions.

@@

I tested whether the priming questions in the relevance treatment condition increased the perceived personal relevance of the two policy plans (in each of the two areas). For this purpose, I relied on the above perceived personal relevance items. Table A1 shows the results of regression analyses. For each of the two policy plans, I first regress perceived personal relevance on the relevance treatment and the areas, and thereafter I add their interaction. Counter to my expectations, the relevance manipulation did not have a positive main effect on either of these two policy plans. Regarding the air-pollution policy, the interaction between the relevance treatment and the center area is positive and significant, and the coefficient of the relevance treatment is negative (model 2). The interpretation of this interaction suggests that the priming questions decreased the perceived personal relevance of the air-pollution policy among Haifa-Bay subjects, but increased it among those who reside in the Center. Regarding the recycling policy, the interaction is insignificant.

@@

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
mod_relevance_air_1.1_apx = lm(RELEVANCE_air_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_relevance_air_1.2_apx = update(mod_relevance_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

mod_relevance_waste_1.1_apx = lm(RELEVANCE_waste_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01_comb)
mod_relevance_waste_1.2_apx = update(mod_relevance_waste_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)

stargazer(mod_relevance_air_1.1_apx,mod_relevance_air_1.2_apx,
          mod_relevance_waste_1.1_apx,mod_relevance_waste_1.2_apx,
          type="html",style = "apsr",
          dep.var.labels=c("Air-pollution","Recycling"),
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients, with Standard errors in parentheses. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)
```

@@

In this section, I report the results of power estimations, which I conducted after collecting and analyzing the data. I have conducted seperate analyses for: (1) Main effects of the symbols and weak information manipulations; (2) Conditional effects of manipulations within each of the two areas (Haifa-Bay and Center); (3) Two-way interactions bewteen areas and the manipulations; and (4) Two-way interactions bewteen the relevance manipulation and the manipulations (in the Haifa-Bay area).

These power estimations were conducted in R software, through regression models simulations with 1,000 interations for each effect size [code adopted from @hughes_website_2017]. All these tests refer to a *p-value* of .05 (one-tailed), with `set.seed(2018)`. These analyses refer to a the analytical sample size (*N* = `r nrow(SVIVA2_01)`, *N*<sub>*Haifa-Bay*</sub>=`r nrow(SVIVA2_01_haifa)`, *N*<sub>*Center*</sub>=`r nrow(SVIVA2_01_center)`). Finally, I assumed that the error term is normally distributed (Mean = 0, SD = 1).

@@

**Figure XX: Power of conditional effects**
```{r, echo=FALSE,warning=FALSE,message=FALSE}

@@

**Figure XX: Power of conditional effects**
```{r, echo=FALSE,warning=FALSE,message=FALSE}
results.conditional %>%
    group_by(cond.effect,
             area,
             effect_sizes) %>%
    summarize(power=sum(p < .1) / n()) %>%

@@

**Figure XX: Power of Interactions with area**
```{r, echo=FALSE,warning=FALSE,message=FALSE}
results.area %>%
    group_by(Interaction,
             effect_sizes) %>%
    summarize(power=sum(p < .1) / n()) %>%

@@

**Figure XX: Power of Interactions with relevance manipulation**

@@

@@

*Table A1* replicates the interaction models in the paper (1.3, 3.2 and 2.3) while restricting the sample to those who saw that policy first before the recycling policy. The directions of the coefficients in these models remain intact. The effect of the real symbols is greater, compared with the full sample (in both policies). This may indicate that the impact of symbols diminishes between the first and the second time participants are exposed to them.

*Table A2* compares between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies: (a) Subjects' city of residence, and its geographical proximity to the polluting industrial area; (b) Parents for young children. The selection of these two variables is driven by the media coverage of the reports published in 2015-6 regarding the air-pollution in the Haifa Bay. The media reports following the publication of the the statistical data of the Ministry of Health in 2015 mostly highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [e.g. @elroi_website_2015; @raavad_website_2015]. Thereafter, reports of the epidemiological study both emphasized the finding regarding the small heads of babies in Haifa Bay, as well as that areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].

For the first proxi, I selected the three cities/suburbs that are closer to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in all other cities in the Haifa Bay sample (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`). The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`). As for the second proxi, I use a binary variable coded 1 for parents for children under 12 years, and 0 otherwise. However, while I expect parents for young children to be more engaged, that assumption is not supported by differences in self-reported perceived personal relevance. In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.

Finally, *Tables A3-A5* replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`). The results of these models latter models do not substantially diverge from the results of the main models.

@@

`r table.x=table.x+1`**Table A`r table.x`: Regression analyses – policy presented first of order.**

```{r,results="asis"}
stargazer(mod_air_1.5, mod_air_null,
          mod_relevance_1.4, mod_relevance_null,
          mod_waste_1.5, mod_waste_null,
          type = "html",
          se  = list(mod_air_1.5.robust_se,NULL,
                     mod_relevance_1.4.robust_se,NULL,
                     mod_waste_1.5.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(1.",1:3,")"),
          column.separate = c(2,2,2),
          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information",
                             "Relevance treatment",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          omit = control.vars,
          p.auto = F,
          add.lines = list(
                           c("Controls","no","","no","","no",""),
                           c("F Statistic", 
                             mod_air_1.5.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.4.wald_results[2,3] %>% round(2),NA,
                             mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
          notes = "",
          notes.append = FALSE)
```

`r table.x=table.x+1`**Table `r table.x`: Regression analyses – moderation of proximity to industrial area and young children.**

@@

@@

@@

stargazer(mod_closedness_1.1,mod_closedness_null,
          mod_closedness_1.2,mod_closedness_null,
          mod_closedness_1.3, mod_closedness_null,
          type = "html",
          se  = list(mod_closedness_1.1.robust_se,NULL,
                     mod_closedness_1.2.robust_se,NULL,
                     mod_closedness_1.3.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(2.",1:4,")"),
          column.separate = c(2,2,2),
          dep.var.labels="Trust in air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Proximity to industrial area",
                             "Young children",
                             "Proximity x Real symbols",
                             "Proximity x Fake symbols",
                             "Proximity x Weak Information",
                             "Young children x Real symbols",
                             "Young children x Fake symbols",
                             "Young children x Weak Information"),          
          p.auto = F,
          add.lines = list(
                           c("Controls","Yes","","Yes","","Yes",""),
                           c("F Statistic", 
                             mod_closedness_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_closedness_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_closedness_1.3.wald_results[2,3] %>% round(2),NA)),
          notes = "",
          notes.append = FALSE)
```

@@

`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – trust in air-pollution policy (unfilterred sample).**

@@

stargazer(mod_air_1.1,mod_air_null,
          mod_air_1.2,mod_air_null,
          mod_air_1.3, mod_air_null,
          mod_air_1.4, mod_air_null,
          type = "html",
          se  = list(mod_air_1.1.robust_se,NULL,
                     mod_air_1.2.robust_se,NULL,
                     mod_air_1.3.robust_se,NULL,
                     mod_air_1.4.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(3.",1:4,")"),
          column.separate = c(2,2,2,2),
          dep.var.labels="Trust in air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.3.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients. Robust standard errors are in parentheses and *p-values* (two-tailed) are reported. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

@@

`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – trust in recycling policy (unfilterred sample).**

@@

stargazer(mod_waste_1.1,mod_waste_null,
          mod_waste_1.2,mod_waste_null,
          mod_waste_1.3, mod_waste_null,
          mod_waste_1.4, mod_waste_null,
          type = "html",
          se  = list(mod_waste_1.1.robust_se,NULL,
                     mod_waste_1.2.robust_se,NULL,
                     mod_waste_1.3.robust_se,NULL,
                     mod_waste_1.4.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(4.",1:4,")"),
          column.separate = c(2,2,2,2),
          dep.var.labels="Trust in recycling policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_waste_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_waste_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_waste_1.3.wald_results[2,3] %>% round(2),NA,
                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA)),
          notes = "*Notes*: Table entries are nonstandardized OLS-regression coefficients. Robust standard errors are in parentheses and *p-values* (two-tailed) are reported. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

@@

`r table.x=table.x+1`**Table a`r table.x`: Regression analyses – experimental manipulation of perceived personal relevance (unfilterred sample).**

@@

[For subjets assigned to the no symbols]:

>>>>

---
title: "Supplementary appendix"
author: '**Saar Alon-Barkat**'
date: " "
output:
  html_document:
    theme: flatly
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
      toc_depth: 3
  pdf_document:
    toc: yes
  word_document: default
link-citations: yes
bibliography: phd_paper_2.bib
urlcolor: blue
---

@@

```{r , include=FALSE, echo=FALSE}
library(knitr)
library(tidyverse)
library(stargazer)
library(car)
library(broom)
library(kableExtra)
library(sjPlot)
library(ggthemes)
library(ggpubr)
library(lmtest)
library(sandwich)
library(effsize)
```

@@

# Characteristics of the selected cities

@@

Notes:
Data for all cities, except for Qiryat-Hayiim, is retrived from the Central Bureau of Statistics data file of local authorities in Israel of 2015. Qiryat-Hayiim is considered, formally, a neighborhood within the jurisdiction of Haifa, although it is geographically separated from the rest of the city. Therefore, it is included in the official statistical data within Haifa. The population of Qiryat-Hayiim is based on a document of statistical data for neighborhoods in Haifa for 2015, retrieved from the website of the municipality of Haifa.

@@

**Figure A3**

@@

**Figure A4**

@@

**Figure A5**
"The person presented in the image is familiar to me" (1=weakly agree; 7=strongly agree)

@@

**Figure A6**

@@

**Figure A7**

@@

**Figure A8**

@@

This section aims to assess the concern that participants did not accept the authenticity of the weak, fictional policy plan, and did not find it reliable, and as a results lost trust in the rest of the survey. To assess that risk, I took advantage of the fact that the order in which the strong and weak policies were presented was randomized. To reiterate, half of the participants saw a weak plan first, and thereafter a strong plan, and for the other half it was the opposite. Hence, I examined whether the the strong policy was evaluated differently when it was presented first (which means that participants at that point did not sea weak policy yet and did not question the reliability of the survey), then when it was presented second (after they already saw a fictional policy). This comparison, across the two policies, is graphically presented in the following plot. It shows that the differences between the means and distributions of the first and the second policy are relatively small and insignificant. The small increase between the first and second round may be explained be the fact that participants used the first (weak) policy as a benchmark, and therefore compared the second policy with the first one. Altogether, these test tend to indicate that participants' exposure to the fictional weak policy did not have a strong influence on their answers to the subsequent questions.

**Figure A9**

@@

I tested whether the priming questions in the relevance treatment condition increased the perceived personal relevance of the two policy plans (in each of the two areas). For this purpose, I relied on the above perceived personal relevance items. Table A1 shows the results of regression analyses. For each of the two policy plans, I first regress perceived personal relevance on the relevance treatment and the areas, and thereafter I add their interaction, and add controls. Counter to my expectations, the relevance manipulation did not have a positive main effect on either of these two policy plans. Regarding the air-pollution policy, the interaction between the relevance treatment and the center area is positive and significant, and the coefficient of the relevance treatment is negative. The interpretation of this interaction suggests that the priming questions slightly decreased the perceived personal relevance of the air-pollution policy among Haifa-Bay subjects, and increased it among those who reside in the Center. Regarding the recycling policy, the interaction is insignificant.

@@

```{r,results="asis",echo=FALSE,warning=FALSE,message=FALSE}
control.vars <- c("GENDER",
                  "AGE",
                  "GOV_TRUST",
                   "IDEOLOGY",
                   "EDUCATION",
                   "INCOME",
                   "CHILDREN",
                   "CHILDREN_young")

mod_relevance_air_null_apx = lm(RELEVANCE_air_obs~1,data=SVIVA2_01)
mod_relevance_air_1.1_apx = lm(RELEVANCE_air_obs~AREA_center+RELEVANCE_exp,data=SVIVA2_01)
mod_relevance_air_1.2_apx = update(mod_relevance_air_1.1_apx,. ~ .+RELEVANCE_exp*AREA_center)
mod_relevance_air_1.3_apx = update(mod_relevance_air_1.2_apx,. ~ .+
                      GENDER+
                       AGE+
                       GOV_TRUST+
                       IDEOLOGY+
                       EDUCATION+
                       INCOME+
                       CHILDREN_young)

mod_relevance_waste_null_apx = lm(RELEVANCE_waste_obs~1,data=SVIVA2_01)
mod_relevance_waste_1.1_apx = update(mod_relevance_air_1.1_apx,RELEVANCE_waste_obs ~ .)
mod_relevance_waste_1.2_apx = update(mod_relevance_air_1.2_apx,RELEVANCE_waste_obs ~ .)
mod_relevance_waste_1.3_apx = update(mod_relevance_air_1.3_apx,RELEVANCE_waste_obs ~ .)

## Adjust standard errors & F statistic
mod_relevance_air_1.1_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_air_1.1_apx, type = "HC1")))
mod_relevance_air_1.1_apx.wald_results <- waldtest(mod_relevance_air_1.1_apx, vcov = vcovHC(mod_relevance_air_1.1_apx, type = "HC1"))

mod_relevance_air_1.2_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_air_1.2_apx, type = "HC1")))
mod_relevance_air_1.2_apx.wald_results <- waldtest(mod_relevance_air_1.2_apx, vcov = vcovHC(mod_relevance_air_1.2_apx, type = "HC1"))

mod_relevance_air_1.3_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_air_1.3_apx, type = "HC1")))
mod_relevance_air_1.3_apx.wald_results <- waldtest(mod_relevance_air_1.3_apx, vcov = vcovHC(mod_relevance_air_1.3_apx, type = "HC1"))

mod_relevance_waste_1.1_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_waste_1.1_apx, type = "HC1")))
mod_relevance_waste_1.1_apx.wald_results <- waldtest(mod_relevance_waste_1.1_apx, vcov = vcovHC(mod_relevance_waste_1.1_apx, type = "HC1"))

mod_relevance_waste_1.2_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_waste_1.2_apx, type = "HC1")))
mod_relevance_waste_1.2_apx.wald_results <- waldtest(mod_relevance_waste_1.2_apx, vcov = vcovHC(mod_relevance_waste_1.2_apx, type = "HC1"))

mod_relevance_waste_1.3_apx.robust_se    <- sqrt(diag(vcovHC(mod_relevance_waste_1.3_apx, type = "HC1")))
mod_relevance_waste_1.3_apx.wald_results <- waldtest(mod_relevance_waste_1.3_apx, vcov = vcovHC(mod_relevance_waste_1.3_apx, type = "HC1"))

stargazer(mod_relevance_air_1.1_apx,mod_relevance_air_null_apx,
          mod_relevance_air_1.2_apx,mod_relevance_air_null_apx,
          mod_relevance_air_1.3_apx,mod_relevance_air_null_apx,
          mod_relevance_waste_1.1_apx,mod_relevance_waste_null_apx,
          mod_relevance_waste_1.2_apx,mod_relevance_waste_null_apx,
          mod_relevance_waste_1.3_apx,mod_relevance_waste_null_apx,
          type = "html",
          se  = list(mod_relevance_air_1.1_apx.robust_se,NULL,
                     mod_relevance_air_1.2_apx.robust_se,NULL,
                     mod_relevance_air_1.3_apx.robust_se,NULL,
                     mod_relevance_waste_1.1_apx.robust_se,NULL,
                     mod_relevance_waste_1.2_apx.robust_se,NULL,
                     mod_relevance_air_1.3_apx.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(1.",1:6,")"),
          column.separate = c(2,2,2,2,2,2),
          dep.var.labels=c("Air-pollution policy","Recycling policy"),
          omit = control.vars,
          covariate.labels=c("Area (0=Haifa-Bay; 1=center)",
                             "Relevance treatment",
                             "Area x Relevance treatment"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","Yes","",
                                        "No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_relevance_air_1.1_apx.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_air_1.2_apx.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_air_1.3_apx.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_waste_1.1_apx.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_waste_1.2_apx.wald_results[2,3] %>% round(2),NA,

mod_relevance_waste_1.3_apx.wald_results[2,3] %>% round(2),NA)),
          notes = "*Notes*: In all regression tables, entries are nonstandardized OLS-regression coefficients. Robust standard errors are in parentheses and *p-values* (two-tailed) are reported. The reference category for the symbols manipulation conditions is the control (no symbols).",
          notes.append = FALSE)

@@

In this section, I report the results of power estimations, which I conducted after collecting and analyzing the data. I have conducted separate analyses for: (1) Main effects of the symbols and weak information manipulations; (2) Conditional effects of manipulations within each of the two areas (Haifa-Bay and Center); (3) Two-way interactions between areas and the manipulations; and (4) Two-way interactions between the relevance manipulation and the manipulations (in the Haifa-Bay area).

These power estimations were conducted in R software, through regression models simulations with 1,000 iterations for each effect size [code adopted from @hughes_website_2017]. All these tests refer to a *p-value* of .05 (one-tailed), with `set.seed(2018)`. These analyses refer to a the analytical sample size (*N* = `r nrow(SVIVA2_01)`, *N*<sub>*Haifa-Bay*</sub>=`r nrow(SVIVA2_01_haifa)`, *N*<sub>*Center*</sub>=`r nrow(SVIVA2_01_center)`). Finally, I assumed that the error term is normally distributed (Mean = 0, SD = 1).

@@

**Figure A10: Power of conditional effects**
```{r, echo=FALSE,warning=FALSE,message=FALSE}

@@

**Figure A11: Power of conditional effects**
```{r, echo=FALSE,warning=FALSE,message=FALSE}
results.conditional %>%
    group_by(cond.effect,
             area,
             effect_sizes) %>%
    summarize(power=sum(p < .1) / n()) %>%

@@

**Figure A12: Power of Interactions with area**
```{r, echo=FALSE,warning=FALSE,message=FALSE}
results.area %>%
    group_by(Interaction,
             effect_sizes) %>%
    summarize(power=sum(p < .1) / n()) %>%

@@

**Figure A13: Power of Interactions with relevance manipulation**

@@

*Table A4*

@@

@@

@@

relevance.areas.close.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area) 
relevance.areas.close.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$close.industrial.area)

relevance.areas.children.t <- t.test(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young) 
relevance.areas.children.d <- cohen.d(SVIVA2_01_haifa$RELEVANCE_air_obs~SVIVA2_01_haifa$CHILDREN_young)

@@

*Table A5* replicates the interaction models in the paper (1.3, 3.2 and 2.3) while restricting the sample to those who saw that policy first before the recycling policy. The directions of the coefficients in these models remain intact. The effect of the real symbols is greater, compared with the full sample (in both policies). This may indicate that the impact of symbols diminishes between the first and the second time participants are exposed to them.

*Table A6* compares between Haifa Bay subjects who are more/less likely to perceive the air-pollution as personally relevant, based on two proxies: (a) Subjects' city of residence, and its geographical proximity to the polluting industrial area; (b) Parents for young children. The selection of these two variables is driven by the media coverage of the reports published in 2015-6 regarding the air-pollution in the Haifa Bay. The media reports following the publication of the the statistical data of the Ministry of Health in 2015 mostly highlighted the conclusion that half of the cases of cancer among children in the area can be associated to air-pollution [e.g. @elroi_website_2015; @raavad_website_2015]. Thereafter, reports of the epidemiological study both emphasized the finding regarding the small heads of babies in Haifa Bay, as well as that areas that are geographically closer to the industrial areas are found to be at higher risk for cancer [@bendavid_website_2016].

For the first proxy, I selected the three cities/suburbs that are closer to the industrial area - *Nesher*, *Qiryat Haiim* and *Qiryat Bialik* (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==1) %>% nrow()`) -- and compared their residents in the sample with those residing in all other cities in the Haifa Bay sample (*n*=`r SVIVA2_01_haifa %>% filter(close.industrial.area==0) %>% nrow()`). The data confirms that residents of these closer cities tended to perceive the air-pollution policy as more personally relevant (Cohen's D = `r relevance.areas.close.d[["estimate"]] %>% round(2) %>% abs()` [`r (relevance.areas.close.d[["conf.int"]][["upper"]]*-1) %>% round(2)`,`r (relevance.areas.close.d[["conf.int"]][["lower"]]*-1) %>% round(2)`], *t* = `r relevance.areas.close.t[["statistic"]] %>% max() %>% round(2) %>% abs()`, *p* = `r relevance.areas.close.t[["p.value"]] %>% max() %>% round(3) %>% abs()`). As for the second proxy, I use a binary variable coded 1 for parents for children under 12 years, and 0 otherwise. However, while I expect parents for young children to be more engaged, that assumption is not supported by differences in self-reported perceived personal relevance. In other models, not shown here, I also directly tested the interaction between the manipulations and the personal relevance subjective measures.

Finally, *Tables A7-A9* replicate Tables 2-4 in the main paper, while adding observations who were filtered, except for those who reported an age under 18 (*n* = `r SVIVA2_00_comb %>% drop_na(TRUST_air_INDEX) %>%  nrow()`). The results of these models latter models do not substantially diverge from the results of the main models.

**Table A5: Regression analyses – policy presented first of order.**

```{r,results="asis"}
stargazer(mod_air_1.5, mod_air_null,
          mod_relevance_1.4, mod_relevance_null,
          mod_waste_1.5, mod_waste_null,
          type = "html",
          se  = list(mod_air_1.5.robust_se,NULL,
                     mod_relevance_1.4.robust_se,NULL,
                     mod_waste_1.5.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(2.",1:3,")"),
          column.separate = c(2,2,2),
          dep.var.labels=c("Trust in air-pollution policy","Trust in recycling policy"),
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information",
                             "Relevance treatment",
                             "Relevance treatment x Real symbols",
                             "Relevance treatment x Fake symbols",
                             "Relevance treatment x Weak Information"),
          omit = control.vars,
          p.auto = F,
          add.lines = list(
                           c("Controls","no","","no","","no",""),
                           c("F Statistic", 
                             mod_air_1.5.wald_results[2,3] %>% round(2),NA,
                             mod_relevance_1.4.wald_results[2,3] %>% round(2),NA,
                             mod_waste_1.5.wald_results[2,3] %>% round(2),NA)),
          notes = "",
          notes.append = FALSE)
```

**Table A6: Regression analyses – moderation of proximity to industrial area and young children.**

@@

stargazer(mod_closedness_1.1,mod_closedness_null,
          mod_closedness_1.2,mod_closedness_null,
          type = "html",
          se  = list(mod_closedness_1.1.robust_se,NULL,
                     mod_closedness_1.2.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(3.",1:2,")"),
          column.separate = c(2,2),
          dep.var.labels="Trust in air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Proximity to industrial area",
                             "Young children",
                             "Proximity x Real symbols",
                             "Proximity x Fake symbols",
                             "Proximity x Weak Information",
                             "Young children x Real symbols",
                             "Young children x Fake symbols",
                             "Young children x Weak Information"),          
          p.auto = F,
          add.lines = list(
                           c("Controls","Yes","","Yes",""),
                           c("F Statistic", 
                             mod_closedness_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_closedness_1.2.wald_results[2,3] %>% round(2),NA)),
          notes = "",
          notes.append = FALSE)
```

@@

**Table A7: Regression analyses – trust in air-pollution policy (unfiltered sample).**

@@

stargazer(mod_air_1.1,mod_air_null,
          mod_air_1.2,mod_air_null,
          mod_air_1.3, mod_air_null,
          mod_air_1.4, mod_air_null,
          type = "html",
          se  = list(mod_air_1.1.robust_se,NULL,
                     mod_air_1.2.robust_se,NULL,
                     mod_air_1.3.robust_se,NULL,
                     mod_air_1.4.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(4.",1:4,")"),
          column.separate = c(2,2,2,2),
          dep.var.labels="Trust in air-pollution policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_air_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.3.wald_results[2,3] %>% round(2),NA,
                             mod_air_1.4.wald_results[2,3] %>% round(2),NA)),
          notes = "",
          notes.append = FALSE)

@@

**Table A8: Regression analyses – trust in recycling policy (unfiltered sample).**

@@

stargazer(mod_waste_1.1,mod_waste_null,
          mod_waste_1.2,mod_waste_null,
          mod_waste_1.3, mod_waste_null,
          mod_waste_1.4, mod_waste_null,
          type = "html",
          se  = list(mod_waste_1.1.robust_se,NULL,
                     mod_waste_1.2.robust_se,NULL,
                     mod_waste_1.3.robust_se,NULL,
                     mod_waste_1.4.robust_se,NULL),
          style = "apsr",
          report = "vcsp",
          omit.stat = c("rsq","ser", "f"),
          initial.zero = FALSE,
          column.labels   = str_c("a(5.",1:4,")"),
          column.separate = c(2,2,2,2),
          dep.var.labels="Trust in recycling policy",
          omit = control.vars,
          covariate.labels=c("Real symbols",
                             "Fake-symbols",
                             "Weak Information",
                             "Area (0=Haifa Bay; 1=center)",
                             "Area x Real symbols",
                             "Area x Fake symbols",
                             "Area x Weak Information"),
          p.auto = F,
          add.lines = list(
                           c("Controls","No","","No","","No","","Yes",""),
                           c("F Statistic", 
                             mod_waste_1.1.wald_results[2,3] %>% round(2),NA,
                             mod_waste_1.2.wald_results[2,3] %>% round(2),NA,
                             mod_waste_1.3.wald_results[2,3] %>% round(2),NA,
                             mod_waste_1.4.wald_results[2,3] %>% round(2),NA)),
          notes = "",
          notes.append = FALSE)

@@

**Table A9: Regression analyses – experimental manipulation of perceived personal relevance (unfiltered sample).**

@@

[For subjects assigned to the no symbols]:
